Title

### 2012-09-24 inc/liouvilles_theorem/liouvilles_theorem.tex
use space between word and \cite

In the transverse dimension, this is consistent with the definition of `coherent fluence' employed by Reed et al.\cite{reed_evolution_2009} for time-resolved electron microscopy and, of course, the spatial emittance of an electron beam\cite{jensen_theoretical_2006,siwick_ultrafast_2002}.

>>>>

In the transverse dimension, this is consistent with the definition of `coherent fluence' employed by Reed et al.\cite{reed_evolution_2009} for time-resolved electron microscopy and, of course, the spatial emittance of an electron beam \cite{jensen_theoretical_2006,siwick_ultrafast_2002}.

### 2012-09-24 inc/ms_model/ms_model.tex
Constant and linear external forces
Split AG model chapter into two different chapters, one for previous efforts and one for my contributions.
(hopefully) clarified some of the notation and explaination of the purely mathematical parts of the extension
use space between word and \cite

\section{Model of Michalik and Sipe}

@@

The $K^{force}$ integrals, related to the internal force of the pulse's Coulombic repulsion, are far more complicated to evaluate.
For more information about the derivation, see \cite{michalik_analytic_2006}.
The final matrices are
\begin{equation}
  K^{force} = 
  \begin{pmatrix}
    k^{force}_{\smallT} & 0 & 0 \\
    0 & k^{force}_{\smallT} & 0 \\
    0 & 0 & k^{force}_{z}
  \end{pmatrix}
\end{equation}
where
\begin{equation}
  k^{force}_{\alpha} = 
  \frac{N e^2}{4\pi\varepsilon_0} \frac{1}{2\pi^{1/2}\sigma_{\alpha}^{1/2}} L_{\alpha}(\xi)
  \begin{pmatrix}
    0 & 1 \\
    1 & \dfrac{2 \gamma_{\alpha}}{\sigma_{\alpha}}
  \end{pmatrix}
\end{equation}
The parameter $\xi$ is the ellipticity parameter, defined as
\begin{equation}
  \xi \equiv \sqrt{\dfrac{\sigma_{z}}{\sigma_{\smallT}}}
\end{equation}
Note that the original paper of Michalik and Sipe contained an error which incorrectly defined $\xi$; this was corrected in an erratum \cite{michalik_erratum:_2008}.
The family of $L$ functions are
\begin{gather}
  L_{\smallT}(\xi) = \frac{3}{2} \left( L(\xi) + \frac{\xi^2 L(\xi) - \xi}{ 1 - \xi^2 } \right) \\
  L_{z}(\xi) = \frac{ 3 \xi^2 }{ \xi^2 - 1} \left( \xi L(\xi) - 1 \right) \\
  L(\xi) = \frac{1}{2} \int_0^{\pi} \frac{1}{1+\xi\sin(\theta)} d\theta
\end{gather}
The integral function $L(\xi)$ can be evaluated to the piecewise function
\begin{equation}
  L(\xi) = 
  \begin{cases}
    \frac{ \arcsin \sqrt{1-\xi^2} }{ \sqrt{1-\xi^2} } & 0 \le \xi \le 1 \\
    \frac{ \ln\left( \xi + \sqrt{\xi^2 - 1} \right) }{ \sqrt{\xi^2 - 1} } & \xi \ge 1
  \end{cases}
\end{equation}
which, although piecewise, is a smooth and well behaved function.

@@

This AG formalism of Michalik and Sipe\cite{michalik_analytic_2006} employs a mean-field approximation in the evolution of the dynamical effect of the electron pulse's internal space-charge field.
This is of course not strictly accurate for a Gaussian charge distribution and the error leads to a distortion of the pulse shape.
Even so, the self-similar AG model of charge bunch dynamics has been benchmarked against particle tracking simulations for a number of electron pulse shapes,\cite{michalik_analytic_2006,michalik_evolution_2009} including the uniform ellipsoid which explicitly features a linear internal space-charge field.\cite{luiten_how_2004}

>>>>

\section{The Analytic Gaussian Model of Michalik and Sipe} \label{sec:ms_model}

@@

The $K^{force}$ integrals, related to the internal force of the pulse's Coulombic repulsion, are far more complicated to evaluate.
For more information about the derivation, see \cite{michalik_analytic_2006}.
The final matrices are
\begin{equation}
  K^{force} = 
  \begin{pmatrix}
    \hat{k}^{force}_{\smallT} & 0 & 0 \\
    0 & \hat{k}^{force}_{\smallT} & 0 \\
    0 & 0 & \hat{k}^{force}_{z}
  \end{pmatrix}
\end{equation}
where
\begin{equation}
  \hat{k}^{force}_{\alpha} = 
  \frac{N e^2}{4\pi\varepsilon_0} \frac{1}{2\pi^{1/2}\sigma_{\alpha}^{1/2}} L_{\alpha}(\xi)
  \begin{pmatrix}
    0 & 1 \\
    1 & \dfrac{2 \gamma_{\alpha}}{\sigma_{\alpha}}
  \end{pmatrix}
\end{equation}
The parameter $\xi$ is the ellipticity parameter, defined as
\begin{equation}
  \xi \equiv \sqrt{\dfrac{\sigma_{z}}{\sigma_{\smallT}}}
\end{equation}
Note that the original paper of Michalik and Sipe contained an error which incorrectly defined $\xi$; this was corrected in an erratum \cite{michalik_erratum:_2008}.
The family of $L$ functions are
\begin{gather}
  L_{\smallT}(\xi) = \frac{3}{2} \left( L(\xi) + \frac{\xi^2 L(\xi) - \xi}{ 1 - \xi^2 } \right) \\
  L_{z}(\xi) = \frac{ 3 \xi^2 }{ \xi^2 - 1} \left( \xi L(\xi) - 1 \right) \\
  L(\xi) = \frac{1}{2} \int_0^{\pi} \frac{1}{1+\xi\sin(\theta)} d\theta
\end{gather}
The integral function $L(\xi)$ can be evaluated to the piecewise function
\begin{equation}
  L(\xi) = 
  \begin{cases}
    \frac{ \arcsin \sqrt{1-\xi^2} }{ \sqrt{1-\xi^2} } & 0 \le \xi \le 1 \\
    \frac{ \ln\left( \xi + \sqrt{\xi^2 - 1} \right) }{ \sqrt{\xi^2 - 1} } & \xi \ge 1
  \end{cases}
\end{equation}
which, although piecewise, is a smooth and well behaved function.

@@

This AG formalism of Michalik and Sipe \cite{michalik_analytic_2006} employs a mean-field approximation in the evolution of the dynamical effect of the electron pulse's internal space-charge field.
This is of course not strictly accurate for a Gaussian charge distribution and the error leads to a distortion of the pulse shape.
Even so, the self-similar AG model of charge bunch dynamics has been benchmarked against particle tracking simulations for a number of electron pulse shapes,\cite{michalik_analytic_2006,michalik_evolution_2009} including the uniform ellipsoid which explicitly features a linear internal space-charge field.\cite{luiten_how_2004}
